\documentclass[twocolumn,12pt]{article}

\title{Chapter 2 Examples}
\author{Amit Jha \and Vinaya Sheni}


\begin{document}

\maketitle

This is example text in the document that I am writing with the help of the book \TeX \ and \LaTeX.
This is 2nd line to show the natual flow.
Tinke et al.\  made double play.
The empty line means a new paragrapdh.The width is covering hapth the page for the reason that its a two column article class.

The page was produced on \today.
If nominated \ldots, I will not serve
This page of \LaTeX\ manual was produced \today.

% emph - emphasized text.

Here is some \emph{emphasized text that emacs also shows nicely}.

You can have \emph{emphasized text \emph{within} emphasized text also}.

Gnus \footnote{Gnu is a big animal} can be quite a gnusance.
However cows \footnote{cow is a big animal too} are not that big of a gnusance.

%formula

A formula is easy to write such has \(x+7y = 9\)

Does \(x  + y \) always equal to \(y+x\)?
Here is subscript and superscript formula -- \(a_1 + b_1 = 2\) superscript \(a^n + b^5 = 89\)

Let $x$ be a prime such that $y > 2x$

\begin{math} x + 3+ y_1 + x^{2y} = 89 \end{math}

\subsection{A Sectioning Command}
\LaTeX automatically generates the section numbers. Blank lines before or after sectiontiing command have no effect.

This is an example of a quotation text
\begin{quote}
  This part is going to be part of a quotation which will basically have some indentation in it.
  This is second line of indented quote
\end{quote}
It is indented on both the margins foe convinience.

Our presidents have been known for their pithy remarks.
\begin{quote}
  The buck stops here \ldots \emph{Harry Truman}

  I am not a crook \ldots \emph{Richard Nixon}

  It's no exaggeration to say that undecided could go one way or the other \ldots \emph{George Bush}
\end{quote}

Our presidents have been known for their pithy remarks.
\begin{quotation}
  The buck stops here \ldots \emph{Harry Truman}

  I am not a crook \ldots \emph{Richard Nixon}

  It's no exaggeration to say that undecided could go one way or the other \ldots \emph{George Bush}
\end{quotation}

\subsection{Lists}
\begin{itemize}
  \item Each List Item is marked with a \emph {label}. The labels in this itemaized list are bullets.
  \item Lists can be nested in one another.
    \begin {enumerate}
    \item This will be a numbered item in the list.
    \item This is another numbered item.
      \begin {enumerate}
      \item this item is within a numbered item which is with a list.
      \end{enumerate}
      
    \end {enumerate}
\end{itemize}

\subsubsection{Description}
Three animals that you should know about are.
\begin{description}
\item[gnat] A small animal found in the North Woods that causes no end of trouble.
\item[gnu] A large animal found in the crossword puzzle that causes no end of trouble.
\item[armadillo] A medium-sized animal named after a medium sized Texas city.
\end{description}

\subsection{Displayed Formulas}
There are two ways to display math formulas.

\[x' + y^{2} = z_{i} ^ {2}\]

and here is same equation numbered.

\begin{equation}
  x' + y^{2} = z_{i} ^ {2}
\end{equation}

\subsection{Declarations}

\end{document}
